% Chapter Template

\chapter{Approximation of CLT Based on Artificial Neural Network} % Main chapter title

\label{Chapter5} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Neural Network Design}
Artificial neural networks(ANN) which heavily inspired by biology and psychology
have been widely used to solve various practical engineering problems in such
areas as pattern recognition, nonlinear regression, data mining, clustering and
prediction. Methods based on complicated mathematical models is of intensive
computation, approximation function evaluation techniques can be employed to
accelerate the calculation process and reduce the computation cost. In order to
solve practical engineering problems in composite material application, classic
laminational theory(CLT) has been proposed which involves many matrix
multiplication and integration calculation. ANN which has been proved is a
reliable tool instead of complicate mathematical model.  The design of neural
network consists of three basic parts: neural network architecture, learning
rules, and training techniques.

The weight training in ANN is to minimize the error function, such as the most
widely used mean square error which calculate the difference  between the
desired and the prediction output values averaged over all examples.
Backpropation algorithm has been successful applied to in many areas, and it's
based on gradient descent. However, this class of algorithms are  plagued by the
possible existance of local minima or "flat spots" and "the curse of
dimensionality". One method to overcome this problem is to adopt EANN's 

\subsection{Architecture}
The inputs of the neural network is consist of four parts: in-plane loading
$N_x$, $N_y$, and $N_{xy}$, design parameters of laminate, two distinct fiber
orientation angle $\theta_1$ and $\theta_2$, ply thickness $t$, total number of
plies $N$; five engineering constants of composite materials, $E_1$, $E_2$, ;
five strength parameters of a unidirectional lamina. There are two outputs in
the neural network, safety factors for MS theory and Tsai-Wu theory, respectively.
\input{Figures/chapter5_neural_network.tex}
\input{Figures/chapter5_figure_angle_ply_laminate.tex}
\input{Figures/chapter5_ann_for_clt.tex}

\section{Approximation Framework}
\subsection{Data Preparation}
\input{Figures/chapter5_table_training_data.tex}
It's implausible to obatain the training data from practial experiments, so CLT
is taken to generate the training data and evaluation data. Three composite
materials are used, as shown in Table \ref{tab:mat}. The fiber orientation range
is from -90 to 90, the number of layers range is from 5 to 200. Assuming the
composite material only subjects to in-plane loading, each component range is
from -90 to 90;

we sample this function to yield 140000 points distributed uniformly over
aboved mentioned ranges as the training data.

\subsection{Training}
\input{Figures/chapter5_figure_ga_and_ann.tex}
\subsection{Evaluation}
\input{Figures/chapter5_table_ann_valuation.tex}
\subsection{Result and Discussion}
\section{Summary}

