\section{Methodology}
\subsection{Objective function}
The optimization problem can be formulated as searching the optimal stacking
sequence of composite laminate.  There are two design variables here, the angles
in the laminate, and the number of layers that each fiber orientation has. The
objective function is formulated as

\begin{equation}
	\begin{split}
    	F  &= 2t_0 \sum_{k=1}^n n_k  \\
    	   &SF_{MS} \geq 0  \\
    	   &SF_{TW} \geq 0 
	\end{split}
\end{equation}

The first term represent the total thickness of the composite laminates, $t_0$ is ply thickness;
$n_k$ is the number of plies in the kth lamina, in which the fiber orientation is $\theta_k$.

The constraints are the safety factor of the material under certain loading, and it should
greater than 1.

\subsection{Encoding}
Due to the simplicity and efficiency of float representation, this encoding
method is implemented to represent a possible solution. 



\subsection{Selection}
The purpose of the selection operator is to chose mating pool to produce
alternative solutions of better fitness. Traditional methods of selecting
strategies only take the fitness of individuals into acount, however, due to 
the existance of constraint, various selection schemes are implemented to
selecet the mating set. Then, the parents of next generation consists of three
groups: proper groups, active groups, and potential groups according to
different selecting methods. 

Proper parents mean individual fullfils the constraint, which are chosen by the individual's
fitnees, individuals with better fitness are more likely to be chosen if they fit the constraint;
active groups means that individual is supposed to be always exist in the parents during the GA,
which are selected by fitness, ignoring the constraint; The individuals from
active group may not correspond to feasible solutions, but their existance
enriches the variety of the gene clips.  Potential groups means that they are likely
to turn into proper individual after a couple of generations, and potential individuals are chosen
by constraint function, the more the individual fulfils the constraint, the more possiblity it will
be selected.


	
\subsection{Crossover}
The crossover operator happens among these three groups. the child of two proper groups are more
likely to be a proper individual which can be used to obtain a better individual. the child of an
active individual and a potential individual can significantly change the gene of active
individual's chromsome, which lets the individual evolved toward a new
direction. The offspring of
two active individuals are more likely to be an active individual, which can maitain the active
group.
\subsection{Mutation}
A mutation direction is imposed on the mutation operator which to make sure the individual evolving
toward the right direction. The mutation direction, denoted by $md$, is a n dimensional vector corresonding to
number of constraints, it is decided by the constraint thresholds $CT_i$ and the current individual's
constraint value, denoted as $CV_i$,  The mutation vector can be obtained by the following formula

$\text{md} = [CT_1, \cdots, CT_{n-1}, CT_n] -  [CV_0, \cdots, CV_{n-1}, CV_n]$

During the operator, the mutation consists of three parts, the length of the chromsome, the angle
of the chromsome, and the number of each angle. Becasue the chromsome's length is positive correlated with the individual's
fitness, the coefficient of length mutation denoted by $C_l$, if $\sum_{i=1}^{N}{CT_i}$ great than
zero, the mutation length is restricted to the range $[0,C_l \sum_{i=1}^{N}{CT_i}]$; if the
$\sum_{i=1}^{N}{CT_i}$ less than zero, the mutation length is restricted to the range
$[0,\sum_{i=1}^{N}{CT_i}]$; Assuming a $[13_6/-27_4]_s$ carbon T300/5308 composite laminate under
the loading $N_{xx} = N_{yy} = 10$ MPa m, the only constraint is the safety factor greater than 1.
Accoring to the Tsai-Wu criterion, its safety factor is 0.0539. So the mutation vector is $[0.941]$,
assuming the coefficient is 20, so the mutation range is from 0 to 18. A random number is generated
from the range $[0, 18]$, supposing the outcome is 13, then a length generator is used to a list,
the it's sum is 13, suppose the list is [5, 8], the laminate after mutation is $[13_{11}/-27_{12}]_s$.


The relationship between the angles in the composite laminate and the chromsome's fitness is
unclear, so the mutation direction of chromsome's angle is random. The coefficient angle mutation is
$C_a$, $[0,C_a \sum_{i=1}^{N}{CT_i}]$

