\documentclass{article}
\begin{document}
Dear Ms. Springer 

\vskip 0.1in
I am writing to submit our manuscript entitled, A technique for constrained optimization of
symmetric laminates using a new variant of the genetic algorithm, for consideration as a Journal of
Reinforced Plastics and Composites research article. We found a new variant of genetic algorithm for constrained
laminate design under various loading cases.


\vskip 0.1in
Given the increasing use of composite material, we believe the work presented in this work will
appeal to readers who interest in polymer-based material and their applications. 

\vskip 0.1in

Each of the authors confirms that this manuscript has not been previously published and is not
currently under consideration by any other journal. Additionally, all of the authors have approved
the contents of this paper and have agreed to the Journal of Reinforced Plastic and Composite submission
policies.

\vskip 0.1in

We would like to suggest the following potential
reviewers because they would have the requisite background to evaluate our findings and
interpretation objectively.

\vskip 0.05in
1.  Chaobin He, Associate Professor, National University of Singapore, Singapore,

	email: msehc@nus.edu.sg 

\vskip 0.02in
2.  Hung-Jue Sue, Professor,  Texas A\&M University, USA 

	email: hjsue@tamu.edu 
\vskip 0.02in

3.  Langley D. Kenneth,  Professor, University of Massachusetts Dartmouth 

	email: klangley@umassd.edu
\vskip 0.05in


Additionally, to the best of our knowledge, the named authors have no conflict of
interest, financial or otherwise.

\vskip 0.15in

Sincerely,

Huiyao Zhang

\vskip 0.2in
Corresponding Author: Atsushi Yokoyama

Institution: Department of Fiber Science and Engineering, Kyoto Institute of Technology,

Address:   Matsugasaki, Sakyo-ku, Kyoto, 606-8585,JAPAN

TEL: 075-724-7754  

FAX:  075-724-7754


\end{document}


