\section{Experiment}
In the previous section we present the details of our strategies for designing an ANN. In
this section, we describe the details of praparation of training set, and validation set.
\subsection{Dataset Preparation}
For compoiste material, it is impossible to obtain massive training data from
practical scenerio.  Therefore, we use classical lamination theory and failure
theory to prepare the training dataset, which follows a two-step procedure to
calculate the strength ratio: first, evaluate the stress and strain according
to classic lamination theory; second, substitue them into the corresponding
equation to get the strength ratio. We repeat this procedure to yield 14000
points uniformly distributed over the domain space.

The range of in-plane loading is from 0 to 120; the range of fiber orientation $\theta$ is from
-90 to 90; ply thickness $t$ is 1.27mm, number of plies range $N$ is from 4 to 120;
Three different material is used in this experiment, as shown in table \ref{tab:mat}.
Figure \ref{tab:traing-data} shows part of the training data.

In order to speeds up the learning and accerlate convergence, the input
atttributes of the dataset are rescaled to between 0 and 1.0 by a linear function.



\input{tab/experiment_training_data}

The ANN training procedure is carried out by optimising the multinomial
logistic regression objective using mini-batch gradient descent\cite{lecun1989backpropagation} with momentum. the batch size is set to 1000,
momentum to 0.9. the learning rate is set to $10^{-2}$.

