

Failure criteria for composite materials are more difficult to predict due to
structural and material complexity in comparison to isotropic materials. The
failure process of composite materials can be regarded from microscopic and
macroscopic points of view. Most popular criteria about the failure of an angle
lamina are in terms of macroscopic failure criteria, which are based on the
tensile, compressive and shear strengths. According to the failure surfaces,
these criteria can be classified into two classes: one is called independent
failure mode criteria which includes the maximum stress failure theory, maximum
strain failure theory because their failure envelope are rectangle; another is
called quadratic polynomial which includes Tsai-Wu, Chamis, Hoffman, and Hill
criteria because their failure surfaces are of ellipsoidal shape. In the present
study, the two most reliable failure criteria are taken, Maximum stress and Tsai-wu.
Both of these two failure criteria are based on the stresses in the local axes
instead of principal normal stresses and maximum shear stresses, and four normal
strength parameters and one shear stress for a unidirectional lamina are
involved. The five strength parameters are

$(\sigma _1^{T})_{ult}= $ ultimate longitudinal tensile strength(in direction 1),

$(\sigma _1^{C})_{ult}= $ ultimate longitudinal compressive strength,

$(\sigma _2^{T})_{ult}= $ ultimate transverse tensile strength,

$(\sigma _2^{C})_{ult}= $ ultimate transverse compressive strength, and

$(\tau_{12})_{ult}= $ and ultimate in-plane shear strength.

\subsection{Maximum stress failure criterion}
Maximum stress(MS) failure theory consists of maximum normal stress theory
proposed by Rankine and maximum shearing stress theory by Tresca. The stresses
applied on a lamina can be resolved into the normal and shear stresses in the
local axes. If any of the normal or shear stresses in the local axes of a lamina
is equal or exceeds the corresponding ultimate strengths of the unidirectional
lamina, the lamina is considered to be failed. That is

$\sigma_1 \geq (\sigma _1^{T})_{ult} $ or $\sigma_1 \leq -(\sigma _1^{C})_{ult}
$,

$\sigma_2 \geq (\sigma _2^{T})_{ult} $ or $\sigma_2 \leq -(\sigma _2^{C})_{ult}
$,

$\tau_{12} \geq (\tau_{12})_{ult} $  or $\tau_{12} \leq -(\tau_{12})_{ult} $.

where $\sigma_1$ and $\sigma_2$ are the normal stresses in the local axes 1 and 2, respectively;
$\tau_{12}$ is the shear stress in the symmetry plane 1-2.

\subsection{Tsai-wu failure criterion}
The TW criterion is one of the most reliable static failure criteria which is derived from the von
Mises yield criterion.  
A lamina is considered to fail
if \begin{equation} \label{eq:tsai_wu}
\begin{split}
	H_1 \sigma_1  & + H_2 \sigma_2 + H_6 \tau_{12} + H_{11}\sigma_1^2 + H_{22} \sigma_2^2 \\
				  & + H_{66}  \tau_{12}^2 + 2H_{12}\sigma_1\sigma_2 < 1
\end{split}
\end{equation}

is violated, where

\begin{equation}
	\begin{split}
		H_{1}&=\frac{1}{\left(\sigma_{1}^{T}\right)_{u l
		t}}-\frac{1}{\left(\sigma_{1}^{C}\right)_{u l t}} \textstyle{,} \\
		H_{11}&=\frac{1}{\left(\sigma_{1}^{T}\right)_{u l t}\left(\sigma_{1}^{C}\right)_{u l t}} \textstyle{,}\\
		H_{2}&=\frac{1}{\left(\sigma_{2}^{T}\right)_{u l t}}-\frac{1}{\left(\sigma_{2}^{C}\right)_{u l t}} \textstyle{,}\\
		H_{22}&=\frac{1}{\left(\sigma_{2}^{T}\right)_{u l t}\left(\sigma_{2}^{C}\right)_{u l t}} \textstyle{,}\\
		H_{66}&=\frac{1}{\left(\tau_{12}\right)_{u l t}^{2}} \textstyle{,}\\
		H_{12}&=-\frac{1}{2} \sqrt{\frac{1}{\left(\sigma_{1}^{T}\right)_{u l
		t}\left(\sigma_{1}^{C}\right)_{u l t}\left(\sigma_{2}^{T}\right)_{u l
		t}\left(\sigma_{2}^{C}\right)_{u l t}}}\textstyle{.}
	\end{split}
\end{equation}

$H_i$ is the strength tensors of the second order; $H_{ij}$ is the strength
tensors of the fourth order. $\sigma_1$ is the applied normal stress in 
direction 1; $\sigma_2$ is the applied normal stress in the direction 2; and
$\tau_{12}$ is the applied in-plane shear stress.





